### 2012-03-29 intention motor representation with corrado sinigaglia/intention and motor action.ppr.r1.final.tex
submitted version of intention and motor representation; new mindreading minimal theory of mind version

\def \ititle {Intention and motor representation in purposive action}
\def \isubtitle {}
\def \iauthor {}
%\def \iauthor {S. Butterfill* \& C. Sinigaglia**
%\\ 
%**Department of Philosophy, University of Warwick
%\\ 
%***Dipartimento di Filosofia, Università degli Studi di Milano}
\def \iemail{s.butterfill@warwick.ac.uk}
%\date{}

\input{$HOME/Documents/submissions/preamble_steve_paper2}
\author{}
\date{}

@@

Cognitive neuroscience frequently depends on inferences of just this type.
\bf
To illustrate, compare imagining seeing an object moving with actually seeing it move. For this comparison we need to distinguish two ways of imagining seeing. There is a way of imagining seeing which phenomenologically is something like seeing except that it does not necessarily involve being receptive to stimuli. This way of imagining seeing, sometimes called `sensory imagining', is commonly distinguished from cognitive ways of imagining seeing which might for example involve thinking about seeing \citep[§2.1]{Gendler:2011_imagination}.%
\footnote{Note that we define this way of imagining seeing in terms of phenomenology and stipulate nothing about the processes and representations involved.  This is essential for our purposes, since we wish to consider evidence for conjectures about the format of representations it involves.}
It is this way of imagining seeing an object move that we wish to compare with actually seeing an object move.  These two have similarities in characteristic performance profile.  For instance, whether an object can be seen all at once depends on its size and distance from the perceiver; strikingly, when subjects imagine seeing an object, whether they can imagine seeing it all at once depends in the same way on size and distance (\citealp{kosslyn:1978_measuring}; \citealp[p.\ 99ff]{kosslyn:1994_image}).  Also, how long it takes to imagine looking over an object depends on the object's subjective size in the same way that how long it would take to actually look over that object would depend on its subjective size \citep{kosslyn:1978_visual}.%
\footnote{These and further examples are discussed by \citet[p.\ 165]{currie:1997_mental}.
} 
Further, imagining seeing something (for example, imagining seeing a visual mask) can modulate and interfere with actually seeing in much the way that actually seeing the thing imagined would \citep{pearson:2008_functional, ishai:1995_common}. The similarities in characteristic performance profile and the particular patterns of interference are good (if non-decisive) reasons to conjecture that imagining seeing and actually seeing involve representations with a common format. This conjecture is indirectly supported by evidence that imagining seeing and actually seeing not only have a common neural basis but also involve similar patterns of cortical activation \citep[e.g.][]{page:2011_erp}.

@@

\rm

@@

\bf

>>>>

\def \ititle {Intention and motor representation in purposive action}
\def \isubtitle {}
\def \iauthor {}
%\def \iauthor {S. Butterfill* \& C. Sinigaglia**
%\\ 
%**Department of Philosophy, University of Warwick, UK
%\\ 
%***Dipartimento di Filosofia, Università degli Studi di Milano, Italia}
%\def \iemail{s.butterfill@warwick.ac.uk}
%\date{}

\input{$HOME/Documents/submissions/preamble_steve_paper2}
%\author{}
\author {S. Butterfill* \& C. Sinigaglia**
\\ 
**Department of Philosophy, University of Warwick, UK
\\ 
***Dipartimento di Filosofia, Università degli Studi di Milano, Italia}
\date{}

@@

Cognitive neuroscience frequently depends on inferences of just this type.
To illustrate, compare imagining seeing an object moving with actually seeing it move. For this comparison we need to distinguish two ways of imagining seeing. There is a way of imagining seeing which phenomenologically is something like seeing except that it does not necessarily involve being receptive to stimuli. This way of imagining seeing, sometimes called `sensory imagining', is commonly distinguished from cognitive ways of imagining seeing which might for example involve thinking about seeing \citep[§2.1]{Gendler:2011_imagination}.%
\footnote{Note that we define this way of imagining seeing in terms of phenomenology and stipulate nothing about the processes and representations involved.  This is essential for our purposes, since we wish to consider evidence for conjectures about the format of representations it involves.}
It is this way of imagining seeing an object move that we wish to compare with actually seeing an object move.  These two have similarities in characteristic performance profile.  For instance, whether an object can be seen all at once depends on its size and distance from the perceiver; strikingly, when subjects imagine seeing an object, whether they can imagine seeing it all at once depends in the same way on size and distance (\citealp{kosslyn:1978_measuring}; \citealp[p.\ 99ff]{kosslyn:1994_image}).  Also, how long it takes to imagine looking over an object depends on the object's subjective size in the same way that how long it would take to actually look over that object would depend on its subjective size \citep{kosslyn:1978_visual}.%
\footnote{These and further examples are discussed by \citet[p.\ 165]{currie:1997_mental}.
} 
Further, imagining seeing something (for example, imagining seeing a visual mask) can modulate and interfere with actually seeing in much the way that actually seeing the thing imagined would \citep{pearson:2008_functional, ishai:1995_common}. The similarities in characteristic performance profile and the particular patterns of interference are good (if non-decisive) reasons to conjecture that imagining seeing and actually seeing involve representations with a common format. This conjecture is indirectly supported by evidence that imagining seeing and actually seeing not only have a common neural basis but also involve similar patterns of cortical activation \citep[e.g.][]{page:2011_erp}.

@@

@@
